Trauma treatment delay

### 2023-12-02 manuscriptlongversion.Rmd
text

## Results

@@

In this study, one of the limitations was the amount of people having
the recorded outcome being quite small, leading to having the variables
being split up into two groups for the logistical regression.
Furthermore, the original plan was to divide RR, SBP and GCS into
revised trauma score (RTS) categories, from 1-4. However, many of the
RTS variables had few to no patients with the observed outcome. This led
to separation in the logistical regression in these variables, referring
to when an outcome variable separates a predictor variable completely,
which occurs when the predictor is only associated with one outcome
value [@OARC]. In the case of these variables, it was only RTS 3 and 4
who had patients with the observed outcome, which left RTS 1 and 2 with
confidence intervals of 0.00 to infinity. This way would have been the
best way to examine these variables, but as that wasn't possible with
this group of patients, we resorted to making these variables
continuous.

The biases that might have been present in this study would be selection
bias and misclassification bias. Our aim is to make this applicable to
the whole trauma patient

@@

Discussing the generalisability of this study, we included the all the
trauma patients treated and Karolinska University Hospital and excluded
40.7% of that population based on that they had not been screened for
ofi. Additional patients were excluded because of missing data, but no
distinct groups except the not screened patients were removed. On that
basis, this population should be a general representation of trauma
patients at the equivalent of a level 1 trauma center, making this study
generalisable.

>>>>

# Results

@@

In this study, one of the limitations was the amount of people having
the recorded outcome being quite small, leading us into having to limit
the amount of variables we wanted to examine. Furthermore, the original
plan was to divide RR, SBP and GCS into revised trauma score (RTS)
categories, from 1-4. However, many of the RTS variables had few to no
patients with the observed outcome. This led to separation in the
logistical regression in these variables, referring to when an outcome
variable separates a predictor variable completely, which occurs when
the predictor is only associated with one outcome value [@OARC]. In the
case of these variables, it was only RTS 3 and 4 who had patients with
the observed outcome, which left RTS 1 and 2 with confidence intervals
of 0.00 to infinity. This way would have been the best way to examine
these variables, but as that wasn't possible with this group of
patients, we resorted to making these variables continuous.

The biases that might have been present in this study would be selection
bias and misclassification bias.

@@

Discussing the generalisability of this study, we included the all the
trauma patients treated and Karolinska University Hospital and excluded
40.7% of that population based on that they had not been screened for
ofi. Additional patients were excluded because of missing data, but no
distinct groups except the not screened patients were removed. On that
basis, this population should be a general representation of trauma
patients at the equivalent of a level 1 trauma center, making this study
generalisable. This is in line with our aim, as it was to make it
applicable to the whole trauma patient population
